SunPy - Python for Solar Physics

### 2014-08-28 1-Introduction.tex
fixes to the FITS citation

A typical workflow begins with a solar physicist manually identifying
a small number of events of interest on the Sun.  This is typically
done in order to investigate in detail the physics of these events
(for example, the large solar flare of 23 July 2002 has Astrophysical
Journal Letters volume 595, dedicated to its analysis).
In this workflow, an event is investigated in depth which requires 
data from many different instruments.
These data are typically provided in many different formats (for
example, FITS (Flexible Image Transport System, \cite{refId0}), CSV, or
binary files), and contain many different types of data (such as
images, lightcurves and spectra).  In addition, the repositories these data reside
in can have different access methods.  This workflow is characterized
by the large number of heterogeneous datasets used in the
investigation of a small number of solar events.

>>>>

A typical workflow begins with a solar physicist manually identifying
a small number of events of interest on the Sun.  This is typically
done in order to investigate in detail the physics of these events
(for example, the large solar flare of 23 July 2002 has Astrophysical
Journal Letters volume 595, dedicated to its analysis).
In this workflow, an event is investigated in depth which requires 
data from many different instruments.
These data are typically provided in many different formats (for
example, FITS (Flexible Image Transport System, \citealt{refId0}), CSV, or
binary files), and contain many different types of data (such as
images, lightcurves and spectra).  In addition, the repositories these data reside
in can have different access methods.  This workflow is characterized
by the large number of heterogeneous datasets used in the
investigation of a small number of solar events.
